### 2023-02-02 definitions.tex
details
Up

A transition system is {\em finitely branching} if all $\post(s)$ are finite. 
\textcolor{blue}{We restrict our attention to finitely branching TSs.}

@@

\begin{proposition}\cite{DBLP:journals/tcs/FinkelS01}
If $S$ is a WSTS with strong monotony and $I \subseteq S$ is an upward-closed set of states, then $\pred(I )$ is upward-closed.
\end{proposition}
\alain{étrange ces deux propositions, l'une suffirait}
\iffalse
Proof. Assume $s \in \pred (I )$. Then $s \rightarrow t$ for some $t \in I $. If now $s' \geq s$ then strong upward-compatibility entails that $s' \rightarrow t'$ for some $t' \geq t$. Then $t' \in I$ and $s' \in \pred(I )$.
\fi
\mathieu{On peut probablement enlever la Proposition $8$ alors. La proposition $9$ étant plus directement pertinente pour les lemmes/preuves (permet d'avoir itérativement $\pred^k(I)$ upward-closed if $I$ upward-closed - for all $k$).}

@@

A downard-closed set $J$ is {\em decidable} if, given $s \in S$, it is decidable whether
$s \in J$. 
\textcolor{red}{Since a downward-closed set does not have an ``upward-basis'' in general, we will demand that membership is decidable.}
\alain{remarque pas claire}
% \textcolor{red}{Do we still demand this ?}
\mathieu{On peut enlever ce point de discussion ici et en discuter de manière plus complête au moment où on discute de SAFE et BAD plus en détail je pense.}

@@

@@

\begin{proof}
We have to show that we can compute a basis of $I^{k+1}$ if we are given a basis of $I^k $. 
Then the
decidability of the stop condition follows directly. Let $B$ be a basis of $I^k$. 
We have
$$I^{k+1} = I \cup \pred(I^k ) = I \cup
\bigcup_{s' \in B}
\pred(\uparrow \{s' \}).$$
\alain{n'est-ce pas $I^{k+1} = I^k \cup \pred(I^k ) = I^k \cup
\bigcup_{s' \in B}
\pred(\uparrow \{s' \}).$ ?}
\mathieu{À strictement parler, c'est  $I^{k+1} = \bigcup_{0 \leq j \leq k+1} \pred^j(I) = 
I \cup \bigcup_{1 \leq j \leq k+1} \pred^j(I) =
I \cup \pred(\bigcup_{0 \leq j \leq k} \pred^j(I))
=  I \cup \pred(I^k)$. Je vais rajouter une remarque au dessus.}

@@

@@

\begin{proposition}\label{reductions}
coverability, $t$-liveness, home state 
%and reachability
 reduce to resilience.
\end{proposition}

@@

\begin{itemize}
\item $J=S= \downarrow S$ et $I=\uparrow x$ then this particular resilience is coverability of $x$ from $s$.
%\item $J=\{s\}$ and $I=\{x\}$ this particular resilience is reachability of $x$ from $s$.

@@

\item the home state problem can be expressed as $\ldots$
\end{itemize}

>>>>

A transition system is {\em finitely branching} if all $\post(s)$ are finite. 
%\textcolor{blue}{We restrict our attention to finitely branching TSs.}

@@

\begin{proposition}\cite{DBLP:journals/tcs/FinkelS01}
If $S$ is a WSTS with strong monotony and $I \subseteq S$ is an upward-closed set of states, then $\pred(I )$ is upward-closed.
\end{proposition}
%\alain{étrange ces deux propositions, l'une suffirait}
\iffalse
Proof. Assume $s \in \pred (I )$. Then $s \rightarrow t$ for some $t \in I $. If now $s' \geq s$ then strong upward-compatibility entails that $s' \rightarrow t'$ for some $t' \geq t$. Then $t' \in I$ and $s' \in \pred(I )$.
\fi
\mathieu{On peut probablement enlever la Proposition $8$ alors. La proposition $9$ étant plus directement pertinente pour les lemmes/preuves (permet d'avoir itérativement $\pred^k(I)$ upward-closed if $I$ upward-closed - for all $k$).}

@@

A downard-closed set $J$ is {\em decidable} if, given $s \in S$, it is decidable whether
$s \in J$. 
\textcolor{red}{Since a downward-closed set does not have an ``upward-basis'' in general, we will demand that membership is decidable.}
% \textcolor{red}{Do we still demand this ?}
\mathieu{On peut enlever ce point de discussion ici et en discuter de manière plus complête au moment où on discute de SAFE et BAD plus en détail je pense.}

@@

\iffalse
\begin{remark}
$I^{k+1} = \bigcup_{0 \leq j \leq k+1} \pred^j(I) = 
I \cup \bigcup_{1 \leq j \leq k+1} \pred^j(I) =
I \cup \pred(\bigcup_{0 \leq j \leq k} \pred^j(I))
=  I \cup \pred(I^k)$.
\end{remark}
\fi

@@

\begin{proof}
We have to show that we can compute a basis of $I^{k+1}$ if we are given a basis of $I^k $. 
Then the
decidability of the stop condition follows directly. Let $B$ be a basis of $I^k$. 
We have
$$I^{k+1} = I \cup \pred(I^k ) = I \cup
\bigcup_{s' \in B}
\pred(\uparrow \{s' \}).$$

@@

\section{Uniform resilience for WSTS}

@@

\begin{proposition}\label{reductions}
coverability are $t$-liveness reduceable to resilience.
%	home state and reachability
\end{proposition}

@@

\begin{itemize}
\item Let us choose $J=S= \downarrow S$ and $I=\uparrow x$ then resilience is equivalent to coverability of $x$ from $s$.
%\item $J=\{s\}$ and $I=\{x\}$ this particular resilience is reachability of $x$ from $s$.

@@

%\item the home state problem can be expressed as $\ldots$
\end{itemize}
